\documentclass{gerin_cv}

\setname{Gerin}{Amalaraj}
\setaddress{Toronto, CA}
\setmobile{437 - 350 - 9740}
\setmail{gerin.amalaraj6@gmail.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/gerin-amalaraj/} %
\setgithubaccount{https://github.com/gerin98} %
\setgithuburl{github.com/gerin98}
\setlinkedinurl{linkedin.com/in/gerin-amalaraj/}
\setdevpostUrl{devpost.com/GerinAmalaraj}
\setdevpostAccount{https://devpost.com/GerinAmalaraj}
\setthemecolor{Red} %you can play with color of the template (red is also nice..)

\begin{document}

%%%%%%%%%%
% Header %
%%%%%%%%%%
\headerview
\vspace{1ex}
\contactHeaderView

%%%%%%%%%%%
% Summary %
%%%%%%%%%%%
\addblocktext{Summary}{%
    I'm a software developer and an Android enthusiast looking to grow and apply my skills developing, scaling and maintaining Android apps.
}

%%%%%%%%%%%%%
% Education %
%%%%%%%%%%%%%
\section{Education} 
    \datedexperience{University of Toronto}{2016 - 2021} 
    \explanation{BASc in Electrical \& Computer Engineering} 
    \explanationdetail{\coloredbullet\ % 
        Graduated with a Certificate in Artificial Intelligence%
        \par%
    }

%%%%%%%%%%%%%%
% Experience %
%%%%%%%%%%%%%%
\section{Experience}
    %
    \datedexperience{Software Engineer II, Flipp}{05/2021 - Present} %
    % Liberty
    \explanationdetail{\coloredbullet\ %
        Lead Android developer on a Pilot project focused on unlocking organic user growth within the US. Iteratively tested and released multiple tactics including related item suggestions, contextual search and personalized content.\par %
    }
    % Global Search Bar
    \explanationdetail{\coloredbullet\ %
        Implemented the Global SearchBar into the Flipp Android App.\par %
    }
    \explanationSubDetail{\coloredbullet\ %
       Led to an increase in search adoption among US users by \textbf{9.5\%} and search usage by \textbf{6.7}\%.\par %
    }
    \explanationSubDetail{\coloredbullet\ %
       Led to a \textbf{29\% MOM} reduction in user complaints on missing content.\par %
    }
    % Other
    \explanationdetail{\coloredbullet\ %
        A strong advocate for trying out new technology and tackling tech debt.\par %
    }
    \explanationSubDetail{\coloredbullet\ %
       Modernized our codebase to become \textbf{50\% Kotlin}.\par %
    }
    \explanationSubDetail{\coloredbullet\ %
       Introduced Kotlin Flows, Coroutines, Hilt, Mockk, KMM and ML Kit into our codebase.\par %
    }
    \explanationSubDetail{\coloredbullet\ %
       Adopted the MVVM architectural patterns for all features. %
    }
    
    \noindent\datedexperience{Associate Software Engineer, Flipp}{05/2019 - 09/2020} %
    % Sharing
    \explanationdetail{\coloredbullet\ %
        Overhauled our Deep Linking architecture and introduced our in-app Sharing feature.\par %
    }
    \explanationSubDetail{\coloredbullet\ %
       Led to an increase of \textbf{327\% YOY} in sharing and \textbf{5000+ app installs} in the first month.\par %
    }
    \explanationSubDetail{\coloredbullet\ %
       Unlocked Deferred Deep Linking and User Attribution capabilities.\par %
    }
    % Coupon Book
    \explanationdetail{\coloredbullet\ %
        Implemented native coupon support on the Android app to render Coupon Books securing \textbf{\$20,000} from retailers.\par %
    }
    % CCPA
    \explanationdetail{\coloredbullet\ %
       Made our app \textbf{CCPA compliant} allowing California users to request and delete their personal data.\par %
    }
     %
    \datedexperience{ESP (Engineering Strategies \& Practices) Intern, Elecsoft Consulting Inc.}{01/2017 - 04/2017} %
    \explanationdetail{\coloredbullet\ %
        Designed a 'smart weight lifting machine' to allow users to count their reps and calories burned on their phone by signing in with a QR code.\par %
    }
    % \explanationdetail{\coloredbullet\ %
    %   Designed a ’smart weight lifting machine’ to allow users to count their reps and calories burned on their phone by signing in with a QR code \par %
    % }
    
%%%%%%%%%%
% Skills %
%%%%%%%%%%
\section{Skills}
    %
    \newcommand{\skillOne}{\createskill{Programming Languages}{ Kotlin \cpshalf Java \cpshalf Python \cpshalf C/C++ }}
    %
    \newcommand{\skillTwo}{\createskill{Frameworks \ \& \ Libraries}{MVVM \cpshalf Coroutines \cpshalf Kotlin FLow \cpshalf Hilt \cpshalf Databinding \cpshalf Epoxy \cpshalf Kotlin Compose }}
    \newcommand{\skillTwoContinued}{\createskill{}{Room DB \cpshalf Retrofit \cpshalf OkHttp \cpshalf Moshi \cpshalf RxJava  \cpshalf KMM \cpshalf Koin}}
    %
    \newcommand{\skillThree}{\createskill{Software Development}{CircleCi \cpshalf Github Actions \cpshalf Firebase \cpshalf Git \cpshalf Agile Methodology}}
    %
    \newcommand{\skillFour}{\createskill{Languages}{\textbf{\emph{Fluent:}} \ \ English \ \ \textbf{\emph{Beginner:}} \ \  French }}
    %
    % List of all skills
    \createskills{\skillOne, \skillTwo, \skillTwoContinued, \skillThree, \skillFour}
    
%%%%%%%%%%%%
% Projects %
%%%%%%%%%%%%
\section{Projects}
    % NewsCast
    \createProjectSection{NewsCast, Android app written in Kotlin}{07/2020} %
    \explanationdetail{\coloredbullet\ %
        A convenient News app designed to showcase Android best practices. Uses MVVM, Coroutines, Databinding, Koin, Retrofit, Moshi, Room and more.\par %
    }
    \explanationdetail{\coloredbullet\ %
        Offers offline reading, search capabilities, multiple language support and a beautiful UX. \par %
    }
    \createProjectLink{https://gerin98.github.io/NewsCast/}{\coloredbullet\ %
        gerin98.github.io/NewsCast
    }

%%%%%%%%%%%%
% Footnote %
%%%%%%%%%%%%
% \createfootnote

\end{document}
